---
title: "p8105_hw6"
author: "Divya Bisht"
date: "11/24/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(modelr)
```

# Problem 1
```{r}
homicide_wp = 
  read_csv(
    "https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv") %>%
  janitor::clean_names() %>% 
  mutate(city_state = str_c(city, state, sep = ", ")) %>%
  mutate(solved = as.numeric(disposition == "Closed by arrest"), 
         victim_age = as.numeric(victim_age)) %>%  
  filter(!city_state == "Dallas, TX", !city_state == "Phoenix, AZ", 
         !city_state == "Kansas City, MO", !city_state == "Tulsa, AL") %>% 
  
  mutate(victim_race = ifelse(victim_race == "White", "Non-White", "White"),
                            fct_relevel(victim_race, "Non-White", "White"))
```

Baltimore only
```{r}
baltimore_homicide = 
  homicide_wp %>%
  filter(city == "Baltimore") %>% 
  select(solved, victim_age, victim_race, victim_sex)
```

```{r}
baltimore_logistic = 
  glm(solved ~ victim_age + victim_sex + victim_race, 
    data = baltimore_homicide, 
    family = binomial())
```

```{r}
baltimore_logistic %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate), 
        conf.low = exp(estimate - 1.96*std.error),
        conf.high = exp(estimate + 1.96*std.error)) %>%
  filter(term == "victim_raceWhite") %>%       
  knitr::kable(digits = 3)
  
```

GLM for each city

```{r}
  homicide_wp %>% 
  group_by(city_state) %>% 
  nest() %>%
  mutate(model = map(data, ~glm(solved ~ victim_age + victim_sex + victim_race, 
    data = ., family = binomial()))) %>% 
  mutate(model = map(model, broom::tidy)) %>% 
  select(-data) %>% 
  unnest() %>%
  mutate(OR = exp(estimate), 
        conf.low = exp(estimate - 1.96*std.error),
        conf.high = exp(estimate + 1.96*std.error)) %>% 
  filter(term == "victim_raceWhite") %>%       
  mutate(city_state = fct_reorder(city_state, OR)) %>%

  ggplot(aes(x = city_state, y = OR), color = OR) +
    geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  coord_flip()
```

Tampla, Florida had the greatest OR for solving homicides while Boston, Massachusetts has the lowest OR for solving homicides when comparing non-whites to whites. 



## Problem 2
```{r}
birth_data = read_csv("./birthweight.csv") %>% 
    janitor::clean_names() %>%
    mutate(babysex = as.factor(babysex), mrace = as.factor(mrace), frace = as.factor(frace))
```

Looking at bwt: 
```{r}
birth_data %>% 
  ggplot(aes(x = ppbmi, y = bwt)) +  
         geom_point() + 
         theme_bw()
```

Model
```{r}
fit = lm(bwt ~ ppbmi + delwt + smoken, data = birth_data)
```

Based on a literature review about about birthweight, I considered using mother’s pre-pregnancy BMI, mother’s weight at delivery (pounds) and average number of cigarettes smoked per day during pregnancy, average number of cigarettes smoked per day during pregnancy. 

-https://www.ncbi.nlm.nih.gov/pubmed/29397484
-https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3640239/
-https://www.ncbi.nlm.nih.gov/pubmed/16260516

```{r}
birth_data %>% 
  add_predictions(fit) %>% 
  add_residuals(fit) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point()
```

```{r}
cv_df = 
  crossv_mc(birth_data, 100) 
```

Two more models: 
```{r}
cv_df = 
  cv_df %>% 
  mutate(lin_mod = map(train, ~lm(bwt ~ ppbmi + delwt + smoken, data = .)),
         birth_length = map(train, ~lm(bwt ~ blength + gaweeks, data = .)),
         head_circ = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex, data = .))) %>% 
  mutate(rmse_lin = map2_dbl(lin_mod, test, ~rmse(model = .x, data = .y)),
         rmse_birth_length = map2_dbl(birth_length, test, ~rmse(model = .x, data = .y)),
         rmse_head_circ = map2_dbl(head_circ, test, ~rmse(model = .x, data = .y))) 

cv_df %>% 
  select(starts_with("rmse")) %>% 
  gather(key = model, value = rmse) %>% 
  mutate(model = str_replace(model, "rmse_", ""),
         model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin()

```

Based on the plot above, the model with the interaction terms seems to be the best model because it has the lowest rmse. 
